Local Spectral Clustering of Density Upper Level Sets

### 2019-05-23 neurips/local_spectral_density_clustering_neurips.tex
Through Sects 4 and 5, DONE

More broadly, density clustering and level set estimation is a well-studied
problem. \citet{polonik1995, rigollet2009} study density clustering under the 
symmetric set difference metric, \citet{tsybakov1997, singh2009} describe
minimax optimal level set estimators under Hausdorff loss and
\citet{hartigan1981, chaudhuri2010} consider consistent estimation of the
cluster tree, to note but a few works. Our goal is not to improve on these
results, nor to offer a better algorithm for level set estimation; indeed, seen as
a density clustering algorithm, PPR has none of the optimality guarantees 
found in the aforementioned works. Instead, our motivation is start with a
widely-used local spectral method, PPR, and to better understand and
characterize the distinctions between those density clusters which are
well-conditioned for PPR, and those which are not.

@@

To motivate these conditions, \citet{zhu2013} show for arbitrary graph $G =
(V,E)$ and subset of vertices $S \subseteq V$, the PPR estimate \smash{$\Cest$}
of subset $S$ satisfies, for a constant $c>0$,
\begin{equation}
\label{eqn: graph_symmetric_set_difference_1}
\vol(\Cest \setminus S; G) + \vol(S \setminus \Cest; G) \leq c \bigl( \Phi(S,G)
\cdot \tau_{\infty}(G[S])\bigr) \vol(S;G),
\end{equation}
where $\Phi(S;G)$ is the normalized cut of $S$ (as defined in \eqref{eqn:
  normalized_cut}), and \smash{$\tau_{\infty}(G[S])$} is called the \emph{mixing
  time} of a random walk over the induced subgraph $G[S]$ (to be defined
precisely later, in \eqref{eqn: mixing_time}).  The left-hand side in
\eqref{eqn:  graph_symmetric_set_difference_1} resembles a (degree-weighted) 
form of the symmetric set difference metric in \eqref{eqn:
  misclassification_rate}.  As we will show in Section \ref{sec:
  analysis}, the conditions \ref{asmp: bounded_density}--\ref{asmp:
  bounded_volume} allow us to upper bound the normalized cut 
\smash{$\Phi(\Csig[\Xbf]; G_{n,r})$}, and the mixing time 
\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}.  (Informally, 
\ref{asmp: cluster_separation}, \ref{asmp: low_noise_density} yield an upper
bound on \smash{$\cut(\Csig[\Xbf]; G_{n,r})$}, and \ref{asmp: bounded_density}
yields a lower bound on \smash{$\vol(\Csig[\Xbf]; G_{n,r})$}; together with 
\ref{asmp: bounded_volume}, this gives an upper bound on the normalized cut.  On 
the other hand, \ref{asmp: bounded_density}, \ref{asmp: embedding} preclude
bottlenecks in the induced subgraph \smash{$G_{n,r}[\Csig[\Xbf]]$}, and combined
with \ref{asmp: embedding}, this leads to an upper bound on the mixing time over 
this subgraph.)

@@

\begin{theorem}
  \label{thm: conductance_upper_bound}
  Fix $\lambda > 0$, and assume $\Cset \in \Cbb_f(\lambda)$ satisfies
  Assumptions \ref{asmp: bounded_density}--\ref{asmp: low_noise_density}, 
  \ref{asmp: bounded_volume} for some $r, \sigma, \lambda_{\sigma}, c_0, \gamma
  > 0$ (no bound on maximum density is needed). Then for any $0 < \delta < 1$,
  $\epsilon > 0$, if 
  \begin{equation}
    \label{eqn: conductance_sample_complexity}
    n \geq \frac{(2+\epsilon)^2\log(3/\delta)}{\epsilon^2}\left(\frac{25}
      {6 \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
  \end{equation}
  then
  \begin{equation}
    \label{eqn: conductance_additive_error_bound}
    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c_1 \frac{d}{\sigma}
    \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon, 
  \end{equation}
  with probability at least $1-\delta$ (where $c_1 > 0$ is a universal constant).
\end{theorem}

@@

\begin{theorem}
  \label{thm: mixing_time_upper_bound}
  Fix $\lambda > 0$, and assume that \smash{$\Cset \in \Cbb_f(\lambda)$}
  satisfies Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding}
  for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, \rho, L > 0$. Then, for
  any \smash{$0 < r < \sigma/2\sqrt{d}$}, with probability 1,
  \begin{equation} 
    \label{eqn: mixing_time_upper_bound}
    \limsup_{n \to \infty}\tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_1
    \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2}
    \log^2\left(\frac{1}{r}\right) + c_2,
  \end{equation}
  for $c_1,c_2 > 0$ universal constants. 
\end{theorem}

@@

We provide numerical experiments to investigate the tightness of our bounds on normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance of \pprspace on the ``two moons'' dataset. For space reasons, we defer details of the experimental settings to the supplement.

\paragraph{Validating theoretical bounds}

\begin{figure}
  \centering
%  \begin{adjustbox}{minipage=\linewidth}
%    \begin{subfigure}{.33\linewidth}
  \includegraphics[width=0.33\textwidth]{example1plots/sample2}
%      \caption{}
%    \end{subfigure}
%    \begin{subfigure}{.33\linewidth}
  \includegraphics[width=0.33\textwidth]{example1plots/sample1}
%      \caption{}
%    \end{subfigure}
%    \begin{subfigure}{.33\linewidth}
      \includegraphics[width=0.33\textwidth]{example1plots/sigma_normalized_cut_plot}
%      \caption{}
%    \end{subfigure}

%    \begin{subfigure}{.33\linewidth}
      \includegraphics[width=0.33\textwidth]{example1plots/sigma_mixing_time_plot}
%      \caption{}
%    \end{subfigure}
    \begin{subfigure}{.33\linewidth}
      \includegraphics[width=\linewidth]{example1plots/diameter_normalized_cut_plot}
      \caption{}
    \end{subfigure}
    \begin{subfigure}{.33\linewidth}
      \includegraphics[width=\linewidth]{example1plots/diameter_mixing_time_plot}
      \caption{}
    \end{subfigure}
    \caption{Samples, empirical results, and theoretical bounds for mixing time
      and normalized cut as diameter and thickness are varied. In (a) and (b),
      points in $\Cset$ are colored in red; points in $\Csig \setminus \Cset$
      are colored in yellow; and remaining points in blue.} 
    \label{fig:fig1}
  \end{adjustbox}
\end{figure}

As we do not provide any theoretical lower bounds, we investigate the tightness of Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound} via simulation. Figure \ref{fig:fig1} compares these theoretical bounds with the empirical quantities \eqref{eqn: normalized_cut} and \eqref{eqn: mixing_time}, as we vary the diameter $\rho$ and thickness $\sigma$ of a cluster $\Cset$. Panels $(a)$ and $(b)$ show the resulting empirical clusters for two different values of $\rho$ and $\sigma$.

Panels $(d)$ and $(f)$ show our theoretical bounds on mixing time tracking closely with empirical mixing time, in both 2 and 3 dimensions.\footnote{Note that we have rescaled all values of theoretical upper bounds by a constant, in order to mask the effect of large universal constants in these bounds. Therefore only comparison of slopes, rather than intercepts, is meaningful.} This provides empirical evidence that the upper bound on mixing time given by Theorem \ref{thm: mixing_time_upper_bound} has the right dependency on both expansion parameter $\sigma$ and diameter $\rho$. The story in panels $(c)$ and $(e)$ is less obvious. We note that while, broadly speaking, the trends do not appear to match, this gap between theory and empirical results seems largest when $\sigma $ and $\rho$ are approximately equal. As the ratio $\rho/\sigma$ grows, we see the slopes of the empirical curves become more similar to those predicted by theory.

\paragraph{Empirical behavior of \ppr}

\begin{figure}
	\centering
	\begin{adjustbox}{minipage=\linewidth}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth,scale = .5]{example2plots/row1_true_density_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{example2plots/row1_ppr_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{example2plots/row1_conductance_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{example2plots/row1_density_cluster}
			\caption{}
		\end{subfigure}

		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{example2plots/row2_true_density_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{example2plots/row2_ppr_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{example2plots/row2_conductance_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{example2plots/row2_density_cluster}
			\caption{}
		\end{subfigure}

		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{example2plots/row3_true_density_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{example2plots/row3_ppr_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{example2plots/row3_conductance_cluster}
			\caption{}
		\end{subfigure}
		\begin{subfigure}{.24\linewidth}
			\includegraphics[width=\linewidth]{example2plots/row3_density_cluster}
			\caption{}
		\end{subfigure}
		\caption{True density (column 1), \pprspace (column 2), normalized cut (column 3) and estimated density (column 4) clusters for 3 different simulated data sets. Seed node for \pprspace denoted by a black cross.}
		\label{fig:fig2}
	\end{adjustbox}
\end{figure}

To drive home the main implications of Theorems \ref{thm: misclassification_rate} and \ref{thm: consistent_recovery_of_density_clusters}, in Figure \ref{fig:fig2} we show the behavior of \ppr, normalized cut, and the density clustering algorithm of \citep{chaudhuri2010} on the well known ``two moons'' dataset (with added 2d Gaussian noise), considered a prototypical success story for spectral clustering algorithms. The first column consists of the empirical density clusters $C_n$ and $C_n'$ for a particular threshold $\lambda$ of the density function; the second column shows the cluster recovered by \ppr; the third column shows the global minimum normalized cut, computed according to the algorithm of \cite{szlam2010}; and the last column shows a cut of the density cluster tree estimator of \citep{chaudhuri2010}.

Figure \ref{fig:fig2} shows the degrading ability of \pprspace to recover density clusters as the two moons become less well-separated. Of particular interest is the fact that \pprspace fails to recover one of the moons even when normalized cut still succeeds in doing so, supporting our claim from Remark \ref{rmk: diameter}. Additionally, we note that a density clustering algorithm recovers a moon even when both \pprspace and normalized cut fail, lending empirical weight to our overall message that \pprspace recovers only geometrically well-conditioned density clusters.

\section{Discussion}
\label{sec: discussion}
For given data, there are an almost limitless number of ways to define what the ``right'' clustering is. We have considered one such notion -- density upper level sets -- and have detailed a set of natural geometric criteria which, when appropriately satisfied, translate to provable bounds on estimation of the cluster by \ppr. We do not, however, provide a theoretical lower bound showing that our geometric conditions are required for successful recovery on an upper level set. Although we investigate the matter empirically, this is a direction for future work.

>>>>

More broadly, density clustering and level set estimation is a well-studied
problem. \citet{polonik1995, rigollet2009} study density clustering under the 
symmetric set difference metric, \citet{tsybakov1997, singh2009} describe
minimax optimal level set estimators under Hausdorff loss and
\citet{hartigan1981, chaudhuri2010} consider consistent estimation of the
cluster tree, to note but a few works. Our goal is not to improve on these
results, nor to offer a better algorithm for level set estimation; indeed, seen as
a density clustering algorithm, PPR has none of the optimality guarantees 
found in the aforementioned works. Instead, our motivation is to start with a 
widely-used local spectral method, PPR, and to better understand and
characterize the distinctions between those density clusters which are
well-conditioned for PPR, and those which are not.

@@

To motivate these conditions, \citet{zhu2013} show for arbitrary graph $G =
(V,E)$ and subset of vertices $S \subseteq V$, the PPR estimate \smash{$\Cest$}
of subset $S$ satisfies, for a constant $c>0$,
\begin{equation}
\label{eqn: graph_symmetric_set_difference_1}
\vol(\Cest \setminus S; G) + \vol(S \setminus \Cest; G) \leq c \bigl( \Phi(S,G)
\cdot \tau_{\infty}(G[S])\bigr) \vol(S;G),
\end{equation}
where $\Phi(S;G)$ is the normalized cut of $S$ (as defined in \eqref{eqn:
  normalized_cut}), and \smash{$\tau_{\infty}(G[S])$} is called the \emph{mixing
  time} of a random walk over the induced subgraph $G[S]$ (to be defined
precisely later, in \eqref{eqn: mixing_time}).  The left-hand side in
\eqref{eqn:  graph_symmetric_set_difference_1} resembles a (degree-weighted) 
form of the symmetric set difference metric in \eqref{eqn:
  misclassification_rate}.  As we will show in Section \ref{sec:
  analysis}, the conditions \ref{asmp: bounded_density}--\ref{asmp:
  bounded_volume} allow us to upper bound the normalized cut 
\smash{$\Phi(\Csig[\Xbf]; G_{n,r})$}, and the mixing time 
\smash{$\tau_{\infty}(G_{n,r}[\Csig[\Xbf]])$}.\footnote{Informally, assumptions  
\ref{asmp: cluster_separation}, \ref{asmp: low_noise_density} yield an upper
bound on \smash{$\cut(\Csig[\Xbf]; G_{n,r})$}, and \ref{asmp: bounded_density}
yields a lower bound on \smash{$\vol(\Csig[\Xbf]; G_{n,r})$}; together with 
\ref{asmp: bounded_volume}, this gives an upper bound on the normalized cut.  On 
the other hand, \ref{asmp: bounded_density}, \ref{asmp: embedding} preclude
bottlenecks in the induced subgraph \smash{$G_{n,r}[\Csig[\Xbf]]$}, and combined
with the upper bound in \ref{asmp: embedding}, this leads to an upper bound on
the mixing time over this subgraph.}

@@

\begin{theorem}
  \label{thm: conductance_upper_bound}
  Fix $\lambda > 0$, and assume $\Cset \in \Cbb_f(\lambda)$ satisfies
  Assumptions \ref{asmp: bounded_density}--\ref{asmp: low_noise_density}, 
  \ref{asmp: bounded_volume} for some $r, \sigma, \lambda_{\sigma}, c_0, \gamma
  > 0$ (no bound on maximum density is needed). Then for any $0 < \delta < 1$,
  $\epsilon > 0$, if 
  \begin{equation}
    \label{eqn: conductance_sample_complexity}
    n \geq \frac{(2+\epsilon)^2\log(3/\delta)}{\epsilon^2}\left(\frac{25}
      {6 \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
  \end{equation}
  then
  \begin{equation}
    \label{eqn: conductance_additive_error_bound}
    \frac{\Phi_{n,r}(\Csig[\Xbf])}{r} \leq c \frac{d}{\sigma}
    \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
      c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon, 
  \end{equation}
  with probability at least $1-\delta$, where $c > 0$ is a universal constant. 
\end{theorem}

@@

\begin{theorem}
  \label{thm: mixing_time_upper_bound}
  Fix $\lambda > 0$, and assume that \smash{$\Cset \in \Cbb_f(\lambda)$}
  satisfies Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding}
  for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, \rho, L > 0$. Then, for
  any \smash{$0 < r < \sigma/2\sqrt{d}$}, with probability 1,
  \begin{equation} 
    \label{eqn: mixing_time_upper_bound}
    \limsup_{n \to \infty}\tau_{\infty}(G_{n,r}[\Csig[\Xbf]]) \leq c_2
    \frac{\Lambda_{\sigma}^4 d^3 \rho^2 L^2}{\lambda_{\sigma}^4 r^2}
    \log^2\left(\frac{1}{r}\right) + c_3,
  \end{equation}
  for $c_2,c_3 > 0$ universal constants. 
\end{theorem}

@@

We provide numerical experiments to investigate the tightness of our bounds on
the normalized cut and mixing time of $\Csig[\Xbf]$, and examine the performance
of PPR on the ``two moons'' dataset. For space reasons, we defer details of the
experimental settings to the supplement.

\begin{figure}[tb]
  \centering
  % \begin{adjustbox}{minipage=\linewidth}
  %   \begin{subfigure}{.33\linewidth}
  \includegraphics[width=0.32\textwidth]{example1plots/sample2}
  % \caption{}
  % \end{subfigure}
  % \begin{subfigure}{.33\linewidth}
  \includegraphics[width=0.32\textwidth]{example1plots/sample1}
  % \caption{}
  % \end{subfigure}
  % \begin{subfigure}{.33\linewidth}
  \includegraphics[width=0.32\textwidth]{example1plots/sigma_normalized_cut_plot}
  % \caption{}
  % \end{subfigure}

  % \begin{subfigure}{.33\linewidth}
  \includegraphics[width=0.32\textwidth]{example1plots/sigma_mixing_time_plot}
  % \caption{}
  % \end{subfigure}
  % \begin{subfigure}{.33\linewidth}
  \includegraphics[width=0.32\textwidth]{example1plots/diameter_normalized_cut_plot}
  % \caption{}
  % \end{subfigure}
  % \begin{subfigure}{.33\linewidth}
  \includegraphics[width=0.32\textwidth]{example1plots/diameter_mixing_time_plot}
  % \caption{}
  % \end{subfigure}
  \caption{\it\small Top left and top middle: samples from a geometrically
    well- and poor-conditioned cluster. The points in $\Cset$ are colored in 
    red, points in $\Csig \setminus \Cset$ are colored in yellow, and the
    remaining points in blue. Other panels: empirical normalized cut and mixing
    time, as a function of $\sigma$ or $\rho$, versus their theoretical upper
    bounds.} 
  \label{fig:fig1}
%  \end{adjustbox}
\end{figure}

\paragraph{Validating theoretical bounds.}  We investigate the tightness of
Theorems \ref{thm: conductance_upper_bound} and \ref{thm:
  mixing_time_upper_bound} via simulation. Figure \ref{fig:fig1} compares our
upper bounds with the actual empirically-computed quantities \eqref{eqn:
  normalized_cut} and \eqref{eqn: mixing_time}, as we vary the diameter $\rho$
and thickness $\sigma$ of a cluster $\Cset$. The top left and top middle panels
display the resulting empirical clusters for two different values of
$\rho,\sigma$.

The bottom left and bottom right panels assure that our mixing  
time upper bounds track closely the empirical mixing time, in both 2 and 3 
dimensions.\footnote{We rescaled all values of theoretical upper
  bounds by a constant, tto mask the effect of large universal constants
  in these bounds. Therefore only the comparison of slopes, rather than
  intercepts, is meaningful.} This provides empirical evidence that Theorem
\ref{thm: mixing_time_upper_bound} has the right dependency on both expansion
parameter $\sigma$ and diameter $\rho$. The story for the normalized cut panels
is less obvious. We remark that while, broadly speaking, the trends do not
appear to match, this gap between theory and empirical results seems largest
when $\sigma $ and $\rho$ are approximately equal. As the ratio $\rho/\sigma$
grows, the slopes of empirical and theoretical curves become more similar.

\paragraph{Empirical behavior of PPR.} In Figure \ref{fig:fig2}, to drive home
the main implications of Theorems \ref{thm: misclassification_rate} and
\ref{thm: consistent_recovery_of_density_clusters}, we show the
behavior of PPR, normalized cut, and the density clustering algorithm of
\citet{chaudhuri2010} on the well known ``two moons'' dataset (with added 2d 
Gaussian noise), considered a prototypical success story for spectral clustering
algorithms. The first column shows the empirical density clusters $C[X]$
and $C'[X]'$ for a particular threshold $\lambda$ of the density function; the 
second column shows the cluster recovered by PPR; the third column shows the
global minimum normalized cut, computed according to the algorithm of
\citet{szlam2010}; and the last column shows a cut of the density cluster tree
estimator of \citet{chaudhuri2010}.  We can see the degrading ability of PPR to
recover density clusters as the two moons become less well-separated. Of 
particular interest is the fact that PPR fails to recover one of the moons even
when normalized cut still succeeds in doing so, supporting our claim from Remark
\ref{rmk: diameter}. Additionally, we note that the Chaudhuri-Dasgupta algorithm 
succeeds even when both PPR and normalized cut fail.  While our main message was
that PPR recovers geometrically well-conditioned density clusters, it would be  
interesting to establish that it \emph{only} recovers such clusters, a point we
return to below.

\begin{figure}
  \centering
  % \begin{adjustbox}{minipage=\linewidth}
  %   \begin{subfigure}{.24\linewidth}
  \includegraphics[width=0.24\textwidth,scale = .5]{example2plots/row1_true_density_cluster}
  % \caption{}
  % \end{subfigure}
  % \begin{subfigure}{.24\linewidth}
  \includegraphics[width=0.24\textwidth]{example2plots/row1_ppr_cluster}
  % \caption{}
  % \end{subfigure}
  % \begin{subfigure}{.24\linewidth}
  \includegraphics[width=0.24\textwidth]{example2plots/row1_conductance_cluster}
  % \caption{}
  % \end{subfigure}
  % \begin{subfigure}{.24\linewidth}
  \includegraphics[width=0.24\textwidth]{example2plots/row1_density_cluster}
  % \caption{}
  % \end{subfigure}

  % \begin{subfigure}{.24\linewidth}
  \includegraphics[width=0.24\textwidth]{example2plots/row2_true_density_cluster}
  % \caption{}
  % \end{subfigure}
  % \begin{subfigure}{.24\linewidth}
  \includegraphics[width=0.24\textwidth]{example2plots/row2_ppr_cluster}
  % \caption{}
  % \end{subfigure}
  % \begin{subfigure}{.24\linewidth}
  \includegraphics[width=0.24\textwidth]{example2plots/row2_conductance_cluster}
  % \caption{}
  % \end{subfigure}
  % \begin{subfigure}{.24\linewidth}
  \includegraphics[width=0.24\textwidth]{example2plots/row2_density_cluster}
  % \caption{}
  % \end{subfigure}

  % \begin{subfigure}{.24\linewidth}
  \includegraphics[width=0.24\textwidth]{example2plots/row3_true_density_cluster}
  % \caption{}
  % \end{subfigure}
  % \begin{subfigure}{.24\linewidth}
  \includegraphics[width=0.24\textwidth]{example2plots/row3_ppr_cluster}
  % \caption{}
  % \end{subfigure}
  % \begin{subfigure}{.24\linewidth}
  \includegraphics[width=0.24\textwidth]{example2plots/row3_conductance_cluster}
  % \caption{}
  % \end{subfigure}
  % \begin{subfigure}{.24\linewidth}
  \includegraphics[width=0.24\textwidth]{example2plots/row3_density_cluster}
  % \caption{}
  % \end{subfigure}
  \caption{\it\small True density (column 1), PPR (column 2), normalized
    cut (column 3) and estimated density (column 4) clusters for 3 different 
    simulated data sets. Seed node for PPR denoted by a black cross.} 
  \label{fig:fig2}
  %\end{adjustbox}
\end{figure}

\section{Discussion}
\label{sec: discussion}

There are an almost limitless number of ways to define what the ``right''
clustering is. In this paper, we have considered one such notion---density upper
level sets---and have detailed a set of natural geometric criteria which, when 
appropriately satisfied, translate to provable bounds on estimation of the
cluster by PPR. We do not, however, provide a theoretical lower bound showing
that our geometric conditions are required for successful recovery on an upper
level set. Although we investigate the matter empirically, this is a direction
for future work.
